Openness and Computational Reproducibility in plant pathology: where do we stand and a way forward

### 2022-06-10 analysis/paper/paper.Rmd
specify iterations and confidence intervals

Models were fit using the `cumulative(link = "logit")` family function for ordinal scale data.
Each model was run for 6000 iterations in four chains with a warmup of 3000 iterations and thinning set to 1.

@@

A test for practical equivalence, `equivalence_test()`, was performed for each model using the contributed R package 'bayestestR' (version `r packageVersion("bayestestR")`) [@Makowski2019] with the Region of Practical Equivalence (ROPE) set to -0.1 to 0.1.

>>>>

Models were fit using the `cumulative(link = "logit")` family function for ordinal scale data.
Each model was run for 10,000 iterations in four chains with a warmup of 3000 iterations and thinning set to 1.

@@

A test for practical equivalence, `equivalence_test()`, was performed for each model using the contributed R package 'bayestestR' (version `r packageVersion("bayestestR")`) [@Makowski2019] with the Region of Practical Equivalence (ROPE) set to -0.1 to 0.1 and confidence interval of 0.95.
